A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-01 tex/codatadp.tex
tuned abstract

\begin{abstract}
Codatatypes naturally capture potentially infinite data structures and
processes. We introduce a decision procedure that combines reasoning about
datatypes and codatatypes. The dual of the acyclicity rule of datatypes is a
bisimilarity rule that identifies observationally equal values. The procedure is
compatible with the Nelson--Oppen combination method and is useful for both
proving and model finding. It has been implemented in the latest version of
CVC4, a modern SMT solver. An evaluation based on problems generated from
Isabelle/HOL theories demonstrates the potential of the procedure in a proving
context.
\end{abstract}

>>>>

\begin{abstract}
Codatatypes naturally capture potentially infinite data structures and
processes. We introduce a decision procedure that combines reasoning about
datatypes and codatatypes. The dual of the acyclicity rule for datatypes is a
bisimilarity rule that identifies observationally equal, possibly cyclic
values. The procedure is compatible with the Nelson--Oppen method
and is useful for both proving and model finding. It has been implemented in the
latest version of CVC4, a modern SMT solver. An evaluation based on problems
generated from Isabelle/HOL theories demonstrates the potential of the procedure
in a proving context.
\end{abstract}
